Live Functional Programming with Typed Holes

### 2018-11-13 fig-complete.tex
added formal statement of every cast being an identity cast in a well-typed and complete internal expression

\begin{lem}[Complete Consistency] If $\tconsistent{\htau_1}{\htau_2}$ and $\isComplete{\htau_1}$ and $\isComplete{\htau_2}$ then $\htau_1 = \htau_2$.
\end{lem}
\begin{proof} By straightforward rule induction. \end{proof}

@@

>>>>

\begin{lem}[Complete Consistency]\label{lem:complete-consistency} If $\tconsistent{\htau_1}{\htau_2}$ and $\isComplete{\htau_1}$ and $\isComplete{\htau_2}$ then $\htau_1 = \htau_2$.
\end{lem}
\begin{proof} By straightforward rule induction. \end{proof}

@@

\begin{lem}[Complete Casts] If $\hasType{\hGamma}{\hDelta}{\dcasttwo{\dexp}{\htau_1}{\htau_2}}$ and $\isComplete{\dcasttwo{\dexp}{\htau_1}{\htau_2}}$ then $\htau_1 = \htau_2$. \end{lem}
\begin{proof} By straightforward rule induction and Lemma~\ref{lem:complete-consistency}. \end{proof}
